---
title: "Nova Report"
subtitle: "Neuzugänge im SLUB-Katalog"
pagetitle: "Nova Report :: SLUB Katalog"
author-meta: "SLUB Dresden"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
lang: "de-DE"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: false
    mathjax: null
    df_print: paged
    css: ["vendor/slub/webdesign-template/css/font.css", "assets/css/custom.css"]
    includes:
      after_body: assets/html/target.html
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = FALSE, error = FALSE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = "..")
```

Zenodo-Community: [SLUB Nova](https://zenodo.org/communities/slub-nova/records) (`slub-nova`)

# Suchserver

## Indexierungen {.tabset}

```{r indexed-records-input}
indexed_records_series <- readRDS("data/indexed-records-series.RDS")
```

### 2022–2024

Gesamtanzahl an Werten: `r sum(indexed_records_series$count)`

```{r indexed-records-plot}
ggplot2::ggplot(indexed_records_series, ggplot2::aes(x = day, y = count)) +
  ggplot2::geom_col() +
  ggplot2::xlab("Indexierungsdatum") +
  ggplot2::ylab("Anzahl Titel") +
  ggplot2::scale_x_date(date_labels = "%Y", date_breaks = "1 year") +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 60, hjust = 1))
```

DOI [10.5281/zenodo.16858259](https://doi.org/10.5281/zenodo.16858259) / [10.5281/zenodo.16881739](https://doi.org/10.5281/zenodo.16881739) / [10.5281/zenodo.16881662](https://doi.org/10.5281/zenodo.16881662)

### 2022

```{r indexed-records2022}
indexed_records_series2022 <- indexed_records_series[grepl("^2022", indexed_records_series$day), ]
```

Gesamtanzahl an Werten: `r sum(indexed_records_series2022$count)`

```{r indexed-records2022-plot}
ggplot2::ggplot(indexed_records_series2022, ggplot2::aes(x = day, y = count)) +
  ggplot2::geom_col() +
  ggplot2::xlab("Indexierungsdatum") +
  ggplot2::ylab("Anzahl Titel") +
  ggplot2::scale_x_date(date_labels = "%Y-%m", date_breaks = "1 month") +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 60, hjust = 1))
```

DOI [10.5281/zenodo.16858259](https://doi.org/10.5281/zenodo.16858259)

### 2023

```{r indexed-records2023}
indexed_records_series2023 <- indexed_records_series[grepl("^2023", indexed_records_series$day), ]
```

Gesamtanzahl an Werten: `r sum(indexed_records_series2023$count)`

```{r indexed-records2023-plot}
ggplot2::ggplot(indexed_records_series2023, ggplot2::aes(x = day, y = count)) +
  ggplot2::geom_col() +
  ggplot2::xlab("Indexierungsdatum") +
  ggplot2::ylab("Anzahl Titel") +
  ggplot2::scale_x_date(date_labels = "%Y-%m", date_breaks = "1 month") +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 60, hjust = 1))
```

DOI [10.5281/zenodo.16881739](https://doi.org/10.5281/zenodo.16881739)

### 2024

```{r indexed-records2024}
indexed_records_series2024 <- indexed_records_series[grepl("^2024", indexed_records_series$day), ]
```

Gesamtanzahl an Werten: `r sum(indexed_records_series2024$count)`

```{r indexed-records2024-plot}
ggplot2::ggplot(indexed_records_series2024, ggplot2::aes(x = day, y = count)) +
  ggplot2::geom_col() +
  ggplot2::xlab("Indexierungsdatum") +
  ggplot2::ylab("Anzahl Titel") +
  ggplot2::scale_x_date(date_labels = "%Y-%m", date_breaks = "1 month") +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 60, hjust = 1))
```

DOI [10.5281/zenodo.16881662](https://doi.org/10.5281/zenodo.16881662)

# Lokalsystem

## Aktivierungen {.tabset}

```{r newitem-records-input}
newitem_records_series <- readRDS("data/newitem-records-series.RDS")
```

### 2022–2024

Gesamtanzahl an Werten: `r sum(newitem_records_series$count)`

```{r newitem-records-plot}
ggplot2::ggplot(newitem_records_series, ggplot2::aes(x = day, y = count)) +
  ggplot2::geom_col() +
  ggplot2::xlab("Aktivierungsdatum") +
  ggplot2::ylab("Anzahl Titel") +
  ggplot2::scale_x_date(date_labels = "%Y", date_breaks = "1 year") +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 60, hjust = 1))
```

DOI [10.5281/zenodo.10179459](https://doi.org/10.5281/zenodo.10179459) / [10.5281/zenodo.10888494](https://doi.org/10.5281/zenodo.10888494) / [10.5281/zenodo.16385159](https://doi.org/10.5281/zenodo.16385159)

### 2022

```{r newitem-records2022}
newitem_records_series2022 <- newitem_records_series[grepl("^2022", newitem_records_series$day), ]
```

Gesamtanzahl an Werten: `r sum(newitem_records_series2022$count)`

```{r newitem-records2022-plot}
ggplot2::ggplot(newitem_records_series2022, ggplot2::aes(x = day, y = count)) +
  ggplot2::geom_col() +
  ggplot2::xlab("Aktivierungsdatum") +
  ggplot2::ylab("Anzahl Titel") +
  ggplot2::scale_x_date(date_labels = "%Y-%m", date_breaks = "1 month") +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 60, hjust = 1))
```

DOI [10.5281/zenodo.10179459](https://doi.org/10.5281/zenodo.10179459)

### 2023

```{r newitem-records2023}
newitem_records_series2023 <- newitem_records_series[grepl("^2023", newitem_records_series$day), ]
```

Gesamtanzahl an Werten: `r sum(newitem_records_series2023$count)`

```{r newitem-records2023-plot}
ggplot2::ggplot(newitem_records_series2023, ggplot2::aes(x = day, y = count)) +
  ggplot2::geom_col() +
  ggplot2::xlab("Aktivierungsdatum") +
  ggplot2::ylab("Anzahl Titel") +
  ggplot2::scale_x_date(date_labels = "%Y-%m", date_breaks = "1 month") +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 60, hjust = 1))
```

DOI [10.5281/zenodo.10888494](https://doi.org/10.5281/zenodo.10888494)

### 2024

```{r newitem-records2024}
newitem_records_series2024 <- newitem_records_series[grepl("^2024", newitem_records_series$day), ]
```

Gesamtanzahl an Werten: `r sum(newitem_records_series2024$count)`

```{r newitem-records2024-plot}
ggplot2::ggplot(newitem_records_series2024, ggplot2::aes(x = day, y = count)) +
  ggplot2::geom_col() +
  ggplot2::xlab("Aktivierungsdatum") +
  ggplot2::ylab("Anzahl Titel") +
  ggplot2::scale_x_date(date_labels = "%Y-%m", date_breaks = "1 month") +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 60, hjust = 1))
```

DOI [10.5281/zenodo.16385159](https://doi.org/10.5281/zenodo.16385159) 

## Erwerbungen {.tabset}

```{r purchase-records-input}
purchase_records_series <- readRDS("data/purchase-records-series.RDS")
```

### 2022–2024

Gesamtanzahl an Werten: `r sum(purchase_records_series$count)`

```{r purchase-records-plot}
ggplot2::ggplot(purchase_records_series, ggplot2::aes(x = day, y = count)) +
  ggplot2::geom_col() +
  ggplot2::xlab("Erwerbungsdatum") +
  ggplot2::ylab("Anzahl Titel") +
  ggplot2::scale_x_date(date_labels = "%Y", date_breaks = "1 year") +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 60, hjust = 1))
```

DOI [10.5281/zenodo.10251277](https://doi.org/10.5281/zenodo.10251277) / [10.5281/zenodo.10888524](https://doi.org/10.5281/zenodo.10888524) / [10.5281/zenodo.16385169](https://doi.org/10.5281/zenodo.16385169)

### 2022

```{r purchase-records2022}
purchase_records_series2022 <- purchase_records_series[grepl("^2022", purchase_records_series$day), ]
```

Gesamtanzahl an Werten: `r sum(purchase_records_series2022$count)`

```{r purchase-records2022-plot}
ggplot2::ggplot(purchase_records_series2022, ggplot2::aes(x = day, y = count)) +
  ggplot2::geom_col() +
  ggplot2::xlab("Erwerbungsdatum") +
  ggplot2::ylab("Anzahl Titel") +
  ggplot2::scale_x_date(date_labels = "%Y-%m", date_breaks = "1 month") +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 60, hjust = 1))
```

DOI [10.5281/zenodo.10251277](https://doi.org/10.5281/zenodo.10251277)

### 2023

```{r purchase-records2023}
purchase_records_series2023 <- purchase_records_series[grepl("^2023", purchase_records_series$day), ]
```

Gesamtanzahl an Werten: `r sum(purchase_records_series2023$count)`

```{r purchase-records2023-plot}
ggplot2::ggplot(purchase_records_series2023, ggplot2::aes(x = day, y = count)) +
  ggplot2::geom_col() +
  ggplot2::xlab("Erwerbungsdatum") +
  ggplot2::ylab("Anzahl Titel") +
  ggplot2::scale_x_date(date_labels = "%Y-%m", date_breaks = "1 month") +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 60, hjust = 1))
```

DOI [10.5281/zenodo.10888524](https://doi.org/10.5281/zenodo.10888524)

### 2024

```{r purchase-records2024}
purchase_records_series2024 <- purchase_records_series[grepl("^2024", purchase_records_series$day), ]
```

Gesamtanzahl an Werten: `r sum(purchase_records_series2024$count)`

```{r purchase-records2024-plot}
ggplot2::ggplot(purchase_records_series2024, ggplot2::aes(x = day, y = count)) +
  ggplot2::geom_col() +
  ggplot2::xlab("Erwerbungsdatum") +
  ggplot2::ylab("Anzahl Titel") +
  ggplot2::scale_x_date(date_labels = "%Y-%m", date_breaks = "1 month") +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 60, hjust = 1))
```

DOI [10.5281/zenodo.16385169](https://doi.org/10.5281/zenodo.16385169)
